Robotic Bicycle Balance Assistance Reduces Probability of Falling When Subjected to Mechanical Perturbations at Low Speeds

### 2024-04-09 main.tex
Right columns in two tables.

\begin{table}
  \centering
  \caption{Logisitic regression coefficient estimates at
    6~\unit{\kilo\meter\per\hour} and gain $k=10$.}
  \label{table:freq-coefs-6}
  \begin{tabular}{llll}
    \toprule
    Variable                                      & Estimate          & Standard error          & p-value          \\
    \midrule
    Intercept                                     & -0.29             & 0.17                    & 0.09             \\
    Angular impulse                               & 1.69              & 0.27                    & 0.00             \\
    Perturbation order                            & -0.77             & 0.22                    & 0.00             \\
    Balance assist state                          & -0.64             & 0.27                    & 0.02             \\
    Roll angle                                    & -0.25             & 0.21                    & 0.24             \\
    Steer angle                                   & -0.14             & 0.21                    & 0.51             \\
    Balance-assist on $\times$ roll angle         & 0.52              & 0.34                    & 0.12             \\
    Balance-assist on $\times$ steer angle        & -0.41             & 0.34                    & 0.22             \\
    Balance-assist on $\times$ angular impulse    & 0.41              & 0.41                    & 0.32             \\
    Balance-assist on $\times$ perturbation order & -0.53             & 0.34                    & 0.12             \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}
  \centering
  \caption{Logisitic regression coefficient estimates at
    10~\unit{\kilo\meter\per\hour} and gain $k=8$.}
  \label{table:freq-coefs}
  \begin{tabular}{llll}
    \toprule
    Variable                                      & Estimate          & Standard error          & p-value \\
    \midrule
    Intercept                                     & -0.24             & 0.16                    & 0.13    \\
    Angular impulse                               & 2.39              & 0.29                    & 0.00    \\
    Perturbation order                            & -1.16             & 0.21                    & 0.00    \\
    Balance-assist on                             & -0.44             & 0.24                    & 0.07    \\
    Roll angle                                    & 0.27              & 0.22                    & 0.22    \\
    Steer angle                                   & -0.37             & 0.24                    & 0.12    \\
    Balance-assist on $\times$ roll angle         & -0.61             & 0.34                    & 0.08    \\
    Balance-assist on $\times$ steer angle        & 0.56              & 0.35                    & 0.11    \\
    Balance-assist on $\times$ angular impulse    & 0.46              & 0.44                    & 0.29    \\
    Balance-assist on $\times$ perturbation order & -0.37             & 0.32                    & 0.25    \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates at
    6~\unit{\kilo\meter\per\hour} and gain $k=10$.}
  \label{table:freq-coefs-6}
  \begin{tabular}{lrrr}
    \toprule
    Variable                                      & Estimate          & Standard error          & p-value          \\
    \midrule
    Intercept                                     & -0.29             & 0.17                    & 0.09             \\
    Angular impulse                               & 1.69              & 0.27                    & 0.00             \\
    Perturbation order                            & -0.77             & 0.22                    & 0.00             \\
    Balance assist state                          & -0.64             & 0.27                    & 0.02             \\
    Roll angle                                    & -0.25             & 0.21                    & 0.24             \\
    Steer angle                                   & -0.14             & 0.21                    & 0.51             \\
    Balance-assist on $\times$ roll angle         & 0.52              & 0.34                    & 0.12             \\
    Balance-assist on $\times$ steer angle        & -0.41             & 0.34                    & 0.22             \\
    Balance-assist on $\times$ angular impulse    & 0.41              & 0.41                    & 0.32             \\
    Balance-assist on $\times$ perturbation order & -0.53             & 0.34                    & 0.12             \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates at
    10~\unit{\kilo\meter\per\hour} and gain $k=8$.}
  \label{table:freq-coefs}
  \begin{tabular}{lrrr}
    \toprule
    Variable                                      & Estimate          & Standard error          & p-value \\
    \midrule
    Intercept                                     & -0.24             & 0.16                    & 0.13    \\
    Angular impulse                               & 2.39              & 0.29                    & 0.00    \\
    Perturbation order                            & -1.16             & 0.21                    & 0.00    \\
    Balance-assist on                             & -0.44             & 0.24                    & 0.07    \\
    Roll angle                                    & 0.27              & 0.22                    & 0.22    \\
    Steer angle                                   & -0.37             & 0.24                    & 0.12    \\
    Balance-assist on $\times$ roll angle         & -0.61             & 0.34                    & 0.08    \\
    Balance-assist on $\times$ steer angle        & 0.56              & 0.35                    & 0.11    \\
    Balance-assist on $\times$ angular impulse    & 0.46              & 0.44                    & 0.29    \\
    Balance-assist on $\times$ perturbation order & -0.37             & 0.32                    & 0.25    \\
    \bottomrule
  \end{tabular}
\end{table}
